\nonstopmode{}
\documentclass[a4paper]{book}
\usepackage[times,inconsolata,hyper]{Rd}
\usepackage{makeidx}
\usepackage[utf8]{inputenc} % @SET ENCODING@
% \usepackage{graphicx} % @USE GRAPHICX@
\makeindex{}
\begin{document}
\chapter*{}
\begin{center}
{\textbf{\huge Package `Coxmos'}}
\par\bigskip{\large \today}
\end{center}
\inputencoding{utf8}
\ifthenelse{\boolean{Rd@use@hyper}}{\hypersetup{pdftitle = {Coxmos: Cox MultiBlock Survival}}}{}
\ifthenelse{\boolean{Rd@use@hyper}}{\hypersetup{pdfauthor = {Pedro Salguero}}}{}
\begin{description}
\raggedright{}
\item[Title]\AsIs{Cox MultiBlock Survival}
\item[Version]\AsIs{1.1.5}
\item[Maintainer]\AsIs{Pedro Salguero }\email{pedsalga@upv.edu.es}\AsIs{}
\item[Description]\AsIs{This software package provides Cox survival analysis for high-dimensional and multiblock datasets. 
It encompasses a suite of functions dedicated from the classical Cox regression to newest analysis,
including Cox proportional hazards model, Stepwise Cox regression, and Elastic-Net Cox regression, 
Sparse Partial Least Squares Cox regression (sPLS-COX) incorporating three distinct strategies, 
and two Multiblock-PLS Cox regression (MB-sPLS-COX) methods. This tool is designed to adeptly handle 
high-dimensional data, and provides tools for cross-validation, plot generation, and additional resources 
for interpreting results. While references are available within the corresponding functions, 
key literature is mentioned below.
Terry M Therneau (2024) <}\url{https://CRAN.R-project.org/package=survival}\AsIs{>,
Noah Simon et al. (2011) <}\Rhref{https://doi.org/10.18637/jss.v039.i05}{doi:10.18637/jss.v039.i05}\AsIs{>,
Philippe Bastien et al. (2005) <}\Rhref{https://doi.org/10.1016/j.csda.2004.02.005}{doi:10.1016/j.csda.2004.02.005}\AsIs{>,
Philippe Bastien (2008) <}\Rhref{https://doi.org/10.1016/j.chemolab.2007.09.009}{doi:10.1016/j.chemolab.2007.09.009}\AsIs{>,
Philippe Bastien et al. (2014) <}\Rhref{https://doi.org/10.1093/bioinformatics/btu660}{doi:10.1093/bioinformatics/btu660}\AsIs{>,
Kassu Mehari Beyene and Anouar El Ghouch (2020) <}\Rhref{https://doi.org/10.1002/sim.8671}{doi:10.1002/sim.8671}\AsIs{>,
Florian Rohart et al. (2017) <}\Rhref{https://doi.org/10.1371/journal.pcbi.1005752}{doi:10.1371/journal.pcbi.1005752}\AsIs{>.}
\item[URL]\AsIs{}\url{https://github.com/BiostatOmics/Coxmos}\AsIs{}
\item[BugReports]\AsIs{}\url{https://github.com/BiostatOmics/Coxmos/issues}\AsIs{}
\item[License]\AsIs{CC BY 4.0}
\item[Encoding]\AsIs{UTF-8}
\item[Roxygen]\AsIs{list(markdown = TRUE)}
\item[RoxygenNote]\AsIs{7.2.3}
\item[biocViews]\AsIs{}
\item[Depends]\AsIs{R (>= 4.1.0),}
\item[Imports]\AsIs{caret,
cowplot,
furrr,
future,
ggrepel,
ggplot2,
ggpubr,
glmnet,
MASS,
mixOmics,
methods,
patchwork,
progress,
purrr,
Rdpack,
scattermore,
stats,
survcomp,
survival,
survminer,
svglite,
tidyr,
utils}
\item[Suggests]\AsIs{ggforce,
grDevices,
knitr,
nsROC,
RColorConesa,
risksetROC,
rmarkdown,
smoothROCtime,
survivalROC}
\item[RdMacros]\AsIs{Rdpack}
\item[LazyData]\AsIs{true}
\item[NeedsCompilation]\AsIs{yes}
\item[VignetteBuilder]\AsIs{knitr}
\end{description}
\Rdcontents{\R{} topics documented:}
